---
title: "Armenia and Georgia"
output:
  word_document: default
  pdf_document: default
---

# Read Me
```{r}
# This R markdown provides all the codes used for "In defence of the nation: Why do churches receive public trust as high as their secular counterparts?" article published in Nations and Nationalism journal. Once you install packages and import data, all codes should work by just clicking "run all" button. 
```


```{r}
# install.packages(c("car", "ggplot2", "stargazer", "writexl", "foreign", "MASS", "Hmisc", "reshape2", "dplyr"))
library(car)
library(ggplot2)
library(stargazer)
library(writexl)
require(foreign)
require(ggplot2)
require(MASS)
require(Hmisc)
require(reshape2)
require(dplyr)
```

# Loading Data: Seven Datasets are Used 
```{r}
library(haven)
EVS_WVS<-read_sav("EVS_WVS_Joint_spss_v3_0.sav")
Georgia2009<-read_sav("WV5_Data_Georgia_Spss_v20201117.sav")
Georgia2014<-read_sav("WV6_Data_Georgia_Spss_v20201117.sav")
Georgia2018<-subset(EVS_WVS, cntry==268)

Armenia2011<-read_sav("WV6_Data_Armenia_Spss_v20201117.sav")
Armenia2018<-subset(EVS_WVS, cntrycow==371)
Armenia2021<-read_sav("WVS_Wave_7_Armenia_Spss_v3.0.sav")
```


# Variables: Georgia 2009 
```{r}
## DV

#trust in religious organizations 
Georgia2009$rel_trust<-Recode(Georgia2009$V131, "4=1; 3=2; 2=3; 1=4")
table(Georgia2009$rel_trust)

## Independent variables 

#Being part of nation 
Georgia2009$part_nation<-Recode(Georgia2009$V212, "4=1; 3=2; 2=3; 1=4")
table(Georgia2009$part_nation)

#Proud of national identity
is.na(Georgia2009$V209) <- which(Georgia2009$V209 ==-1)
is.na(Georgia2009$V209) <- which(Georgia2009$V209 ==-2)
Georgia2009$proud_nation<-Recode(Georgia2009$V209, "1=4; 2=3; 3=2; 4=1")
table(Georgia2009$proud_nation)


## CONTROLS 

#importance of religion in life 
table(Georgia2009$V9)
Georgia2009$importance_rel<-Recode(Georgia2009$V9, "1=4; 2=3; 3=2; 4=1")
table(Georgia2009$importance_rel)

#Interpersonal trust 
Georgia2009$inter_trust<-Georgia2009$V47
table(Georgia2009$inter_trust)

#Membership to religious organizations 
table(Georgia2009$V185b)
Georgia2009$rel_member<-Recode(Georgia2009$V185b, "1e+07=0;30100000=1;30202001=0; 4e+07=0; 5e+07=0; 6e+07=0; 7e+07=0;80213304=0; 90600000=0; 100000020=0")
table(Georgia2009$rel_member)

#Income level
Georgia2009$income<-Georgia2009$V253

#education level
table(Georgia2009$V238)
Georgia2009$educ<-Recode(Georgia2009$V238, "2=1; 3=2; 4=3; 5=4; 6=5; 7=6; 8=7; 9=8")
table(Georgia2009$educ)

#religiosity
Georgia2009$religiosity<-Recode(Georgia2009$V186, "7=1; 6=2; 5=3; 4=4; 3=5; 2=6; 1=7")
table(Georgia2009$religiosity)


#importance of traditions
Georgia2009$important_trad<-Recode(Georgia2009$V89, "6=1; 5=2; 4=3; 3=4; 2=5; 1=6")
table(Georgia2009$important_trad)

#trust in Police
table(Georgia2009$V136)
Georgia2009$trust_police<-Recode(Georgia2009$V136, "4=1; 3=2; 2=3; 1=4")
table(Georgia2009$trust_police)

#Trust in Government 
table(Georgia2009$V138)
Georgia2009$trust_gov<-Recode(Georgia2009$V138, "4=1; 3=2; 2=3; 1=4")
table(Georgia2009$trust_gov)

#Trust in Court
table(Georgia2009$V137)
Georgia2009$trust_court<-Recode(Georgia2009$V137, "4=1; 3=2; 2=3; 1=4")
table(Georgia2009$trust_court)

#Trust in Parliament
table(Georgia2009$V140)
Georgia2009$trust_par<-Recode(Georgia2009$V140, "4=1; 3=2; 2=3; 1=4")
table(Georgia2009$trust_par)

#Gender
table(Georgia2009$V235)
Georgia2009$gender<-Georgia2009$V235

#Age
table(Georgia2009$V237)
Georgia2009$age<-Georgia2009$V237

#Urban
table(Georgia2009$V255)
Georgia2009$urban<-Georgia2009$V255

#Prayer
table(Georgia2009$V193)
Georgia2009$pray<-Recode(Georgia2009$V193, "2=0")
```


# Variables:Georgia 2014
```{r}
## DV

#trust in religious organizations 
table(Georgia2014$V108)
Georgia2014$rel_trust<-Recode(Georgia2014$V108, "1=4; 2=3; 3=2; 4=1")
table(Georgia2014$rel_trust)

## IVs 

#Being part of nation 
table(Georgia2014$V214)
Georgia2014$part_nation<-Recode(Georgia2014$V214, "1=3; 2=2; 3=1;")
table(Georgia2014$part_nation)

#Proud of national identity
is.na(Georgia2014$V211) <- which(Georgia2014$V211 ==5)
Georgia2014$proud_nation<-Recode(Georgia2014$V211, "1=4; 2=3; 3=2; 4=1")
table(Georgia2014$proud_nation)


## CONTROLS 

#importance of religion in life 
table(Georgia2014$V9)
Georgia2014$importance_rel<-Recode(Georgia2014$V9, "1=4; 2=3; 3=2; 4=1")
table(Georgia2014$importance_rel)

#Interpersonal trust 
table(Georgia2014$V56)
Georgia2014$inter_trust<-Georgia2014$V56


#Membership to religious organizations 
table(Georgia2014$V144)
Georgia2014$rel_member<-Recode(Georgia2014$V144, "1e+07=0;2e+07=0;30100000=1;30107000=0;5e+07=0;80213304=0;80400035=0;90600000=0;100000020=0")
table(Georgia2014$rel_member)



#Income level
table(Georgia2014$V239)
Georgia2014$income<-Georgia2014$V239


#education level
table(Georgia2014$V248)
Georgia2014$educ<-Recode(Georgia2014$V248, "2=1; 3=2; 4=3; 5=4; 6=5; 7=6; 8=7; 9=8")
table(Georgia2014$educ)

#religiosity
table(Georgia2014$V145)
Georgia2014$religiosity<-Recode(Georgia2014$V145, "7=1; 6=2; 5=3; 4=4; 3=5; 2=6; 1=7")
table(Georgia2014$religiosity)


#importance of traditions
table(Georgia2014$V79)
Georgia2014$important_trad<-Recode(Georgia2014$V79, "6=1; 5=2; 4=3; 3=4; 2=5; 1=6")
table(Georgia2014$important_trad)

#trust in Police
table(Georgia2014$V113)
Georgia2014$trust_police<-Recode(Georgia2014$V113, "4=1; 3=2; 2=3; 1=4")
table(Georgia2014$trust_police)

#Trust in Government 
table(Georgia2014$V115)
Georgia2014$trust_gov<-Recode(Georgia2014$V115, "4=1; 3=2; 2=3; 1=4")
table(Georgia2014$trust_gov)

#Trust in Court
table(Georgia2014$V114)
Georgia2014$trust_court<-Recode(Georgia2014$V114, "4=1; 3=2; 2=3; 1=4")
table(Georgia2014$trust_court)

#Trust in Parliament
table(Georgia2014$V117)
Georgia2014$trust_par<-Recode(Georgia2014$V117, "4=1; 3=2; 2=3; 1=4")
table(Georgia2014$trust_par)

#Gender
table(Georgia2014$V240)
Georgia2014$gender<-Georgia2014$V240

#Age
table(Georgia2014$V242)
Georgia2014$age<-Georgia2014$V242

#Urban
Georgia2014$urban<-Recode(Georgia2014$V253_CS,"268012=0; 268005=1; 268011=1")
table(Georgia2014$urban)

#Praying
table(Georgia2014$V146)
Georgia2014$pray<-Recode(Georgia2014$V146, "1=8; 2=7;3=6;4=5;5=4;6=3;7=2;8=1")
```

# Variables Georgia 2018
```{r}
## DV

#trust in religious organizations: -2:no answer, -1:do not know. 
table(Georgia2018$E069_01)
is.na(Georgia2018$E069_01) <- which(Georgia2018$E069_01 ==-1)
is.na(Georgia2018$E069_01) <- which(Georgia2018$E069_01 ==-2)
Georgia2018$rel_trust<-Recode(Georgia2018$E069_01, "1=4; 2=3; 3=2; 4=1")
table(Georgia2018$rel_trust)

## IV

#Proud of national identity; -3:not applicable, -1: do not know
table(Georgia2018$G006)
is.na(Georgia2018$G006) <- which(Georgia2018$G006 ==-1)
is.na(Georgia2018$G006) <- which(Georgia2018$G006 ==-3)
Georgia2018$proud_nation<-Recode(Georgia2018$G006, "1=4; 2=3; 3=2; 4=1")
table(Georgia2018$proud_nation)


## CONTROLS 

#importance of religion in life.-2:no answer, -1:do not know.   
table(Georgia2018$A006)
is.na(Georgia2018$A006) <- which(Georgia2018$A006 ==-1)
is.na(Georgia2018$A006) <- which(Georgia2018$A006 ==-2)
Georgia2018$importance_rel<-Recode(Georgia2018$A006, "1=4; 2=3; 3=2; 4=1")
table(Georgia2018$importance_rel)

#Interpersonal trust. 1: Most people can be trusted, 2: Can´t be too careful 
table(Georgia2018$A165)
is.na(Georgia2018$A165) <- which(Georgia2018$A165 ==-1)
is.na(Georgia2018$A165) <- which(Georgia2018$A165 ==-2)
Georgia2018$inter_trust<-Recode(Georgia2018$A165, "2=0")
table(Georgia2018$inter_trust)

#Membership to religious organizations 
table(Georgia2018$F025)
is.na(Georgia2018$F025) <- which(Georgia2018$F025 ==-1)
is.na(Georgia2018$F025) <- which(Georgia2018$F025 ==-2)
Georgia2018$rel_member<-Recode(Georgia2018$F025, "0=0;1=0;2=0; 3=1; 5=0;9=0")
table(Georgia2018$rel_member)

#Income level
table(Georgia2018$X047E_EVS5)
is.na(Georgia2018$X047E_EVS5) <- which(Georgia2018$X047E_EVS5 ==-1)
is.na(Georgia2018$X047E_EVS5) <- which(Georgia2018$X047E_EVS5 ==-2)
Georgia2018$income<-Georgia2018$X047E_EVS5
table(Georgia2018$income)

#education level
table(Georgia2018$X025A_01)
is.na(Georgia2018$X025A_01) <- which(Georgia2018$X025A_01==-2)
Georgia2018$educ<-Georgia2018$X025A_01
table(Georgia2018$educ)

#religiosity: attending religious services 
table(Georgia2018$F028)
is.na(Georgia2018$F028) <- which(Georgia2018$F028 ==-1)
Georgia2018$religiosity<-Recode(Georgia2018$F028, "8=1; 7=2; 6=3; 5=4; 4=5; 3=6; 2=7; 1=8")
table(Georgia2018$religiosity)

#trust in Police
table(Georgia2018$E069_06)
is.na(Georgia2018$E069_06) <- which(Georgia2018$E069_06 ==-1)
is.na(Georgia2018$E069_06) <- which(Georgia2018$E069_06 ==-2)
Georgia2018$trust_police<-Recode(Georgia2018$E069_06, "4=1; 3=2; 2=3; 1=4")
table(Georgia2018$trust_police)

#Trust in Government 
table(Georgia2018$E069_11)
is.na(Georgia2018$E069_11) <- which(Georgia2018$E069_11 ==-1)
is.na(Georgia2018$E069_11) <- which(Georgia2018$E069_11 ==-2)
Georgia2018$trust_gov<-Recode(Georgia2018$E069_11, "4=1; 3=2; 2=3; 1=4")
table(Georgia2018$trust_gov)

#Trust in Court
table(Georgia2018$E069_17)
is.na(Georgia2018$E069_17) <- which(Georgia2018$E069_17 ==-1)
is.na(Georgia2018$E069_17) <- which(Georgia2018$E069_17 ==-2)
Georgia2018$trust_court<-Recode(Georgia2018$E069_17, "4=1; 3=2; 2=3; 1=4")
table(Georgia2018$trust_court)

#Trust in Parliament
table(Georgia2018$E069_07)
is.na(Georgia2018$E069_07) <- which(Georgia2018$E069_07 ==-1)
is.na(Georgia2018$E069_07) <- which(Georgia2018$E069_07 ==-2)
Georgia2018$trust_par<-Recode(Georgia2018$E069_07, "4=1; 3=2; 2=3; 1=4")
table(Georgia2018$trust_par)

#Gender
table(Georgia2018$X001)
Georgia2018$gender<-Georgia2018$X001

#Age
table(Georgia2018$X003)
Georgia2018$age<-Georgia2018$X003

#Urban
table(Georgia2018$size_5c)
Georgia2018$urban<-Georgia2018$size_5c

#Praying
table(Georgia2018$F066_EVS5)
is.na(Georgia2018$F066_EVS5) <- which(Georgia2018$F066_EVS5==-1)
is.na(Georgia2018$F066_EVS5) <- which(Georgia2018$F066_EVS5==-2)
Georgia2018$pray<-Recode(Georgia2018$F066_EVS5, "1=7;2=6;3=5;4=4;5=3;6=2;7=1")
table(Georgia2018$pray)
```


# Variables:Armenia 2011
```{r}
## DV

#trust in religious organizations 
table(Armenia2011$V108)
Armenia2011$rel_trust<-Recode(Armenia2011$V108, "1=4; 2=3; 3=2; 4=1")
table(Armenia2011$rel_trust)

## IVs 

#Proud of national identity
table(Armenia2011$V211)
is.na(Armenia2011$V211) <- which(Armenia2011$V211==5)
Armenia2011$proud_nation<-Recode(Armenia2011$V211, "1=4; 2=3; 3=2; 4=1")
table(Armenia2011$proud_nation)

#Part of Nation
table(Armenia2011$V214)
Armenia2011$part_nation<-Recode(Armenia2011$V214, "1=4; 2=3; 3=2; 4=1")
table(Armenia2011$part_nation)



## CONTROLS 

#importance of religion in life 
table(Armenia2011$V9)
Armenia2011$importance_rel<-Recode(Armenia2011$V9, "1=4; 2=3; 3=2; 4=1")
table(Armenia2011$importance_rel)

#Interpersonal trust 
table(Armenia2011$V24)
Armenia2011$inter_trust<-Recode(Armenia2011$V24, "2=0")

#Membership to religious organizations 
table(Armenia2011$V144)
Armenia2011$rel_member<-Recode(Armenia2011$V144, "1e+07=0; 2e+07=0; 10100000=0; 4e+07=0; 3e+07=0; 7e+07=0; 30202001=1;30107000=0;30100000=0;90800000=0;  5e+07=0; 80213304=0; 80400035=0; 90600000=0; 100000020=0; 9e+07=0")
table(Armenia2011$rel_member)

#Income level
table(Armenia2011$V239)
Armenia2011$income<-Armenia2011$V239

#education level
table(Armenia2011$V248)
Armenia2011$educ<-Armenia2011$V248
table(Armenia2011$educ)

#religiosity: attending religious services 
table(Armenia2011$V145)
Armenia2011$religiosity<-Recode(Armenia2011$V145, "7=1; 6=2; 5=3; 4=4; 3=5; 2=6; 1=7")
table(Armenia2011$religiosity)

#importance of traditions
table(Armenia2011$V79)
Armenia2011$important_trad<-Recode(Armenia2011$V79, "6=1; 5=2; 4=3; 3=4; 2=5; 1=6")
table(Armenia2011$important_trad)

#trust in Police
table(Armenia2011$V113)
Armenia2011$trust_police<-Recode(Armenia2011$V113, "4=1; 3=2; 2=3; 1=4")
table(Armenia2011$trust_police)

#Trust in Government 
table(Armenia2011$V115)
Armenia2011$trust_gov<-Recode(Armenia2011$V115, "4=1; 3=2; 2=3; 1=4")
table(Armenia2011$trust_gov)

#Trust in Court
table(Armenia2011$V114)
Armenia2011$trust_court<-Recode(Armenia2011$V114, "4=1; 3=2; 2=3; 1=4")
table(Armenia2011$trust_court)

#Trust in Parliament
table(Armenia2011$V117)
Armenia2011$trust_par<-Recode(Armenia2011$V117, "4=1; 3=2; 2=3; 1=4")
table(Armenia2011$trust_par)


#Gender
table(Armenia2011$V240)
Armenia2011$gender<-Armenia2011$V240

#Age
table(Armenia2011$V242)
Armenia2011$age<-Armenia2011$V242

#Urban: town size in rising
table(Armenia2011$V253)
Armenia2011$urban<-Armenia2011$V253

#Praying
table(Armenia2011$V146)
Armenia2011$pray<-Recode(Armenia2011$V146, "1=8; 2=7;3=6;4=5;5=4;6=3;7=2;8=1")
```


# Variables: Armenia 2018
```{r}
## DV

#trust in religious organizations: -2:no answer, -1:do not know. 
table(Armenia2018$E069_01)
Armenia2018$rel_trust<-Recode(Armenia2018$E069_01, "1=4; 2=3; 3=2; 4=1")
table(Armenia2018$rel_trust)

## IV

#Proud of national identity; -3:not applicable, -1: do not know
table(Armenia2018$G006)
Armenia2018$proud_nation<-Recode(Armenia2018$G006, "1=4; 2=3; 3=2; 4=1")
table(Armenia2018$proud_nation)


## CONTROLS 

#importance of religion in life.-2:no answer, -1:do not know.   
table(Armenia2018$A006)
Armenia2018$importance_rel<-Recode(Armenia2018$A006, "1=4; 2=3; 3=2; 4=1")
table(Armenia2018$importance_rel)

#Interpersonal trust. 1: Most people can be trusted, 2: Can´t be too careful 
table(Armenia2018$A165)
Armenia2018$inter_trust<-Recode(Armenia2018$A165, "2=0")
table(Armenia2018$inter_trust)

#Membership to religious organizations 
table(Armenia2018$F025)
Armenia2018$rel_member<-Recode(Armenia2018$F025, "0=0;1=0;2=0; 3=1; 5=0;9=0")
table(Armenia2018$rel_member)

#Income level
table(Armenia2018$X047_WVS7)
Armenia2018$income<-Armenia2018$X047_WVS7
table(Armenia2018$income)

#education level
table(Armenia2018$X025A_01)
Armenia2018$educ<-Armenia2018$X025A_01
table(Armenia2018$educ)

#religiosity: attending religious services 
table(Armenia2018$F028)
Armenia2018$religiosity<-Recode(Armenia2018$F028, "8=1; 7=2; 6=3; 5=4; 4=5; 3=6; 2=7; 1=8")
table(Armenia2018$religiosity)


#trust in Police
table(Armenia2018$E069_06)
Armenia2018$trust_police<-Recode(Armenia2018$E069_06, "4=1; 3=2; 2=3; 1=4")
table(Armenia2018$trust_police)

#Trust in Government 
table(Armenia2018$E069_11)
Armenia2018$trust_gov<-Recode(Armenia2018$E069_11, "4=1; 3=2; 2=3; 1=4")
table(Armenia2018$trust_gov)

#Trust in Court
table(Armenia2018$E069_17)
Armenia2018$trust_court<-Recode(Armenia2018$E069_17, "4=1; 3=2; 2=3; 1=4")
table(Armenia2018$trust_court)

#Trust in Parliament
table(Armenia2018$E069_07)
Armenia2018$trust_par<-Recode(Armenia2018$E069_07, "4=1; 3=2; 2=3; 1=4")
table(Armenia2018$trust_par)

#Gender
table(Armenia2018$X001)
Armenia2018$gender<-Armenia2018$X001

#Age
table(Armenia2018$X003)
Armenia2018$age<-Armenia2018$X003

#Urban
table(Armenia2018$size_5c)
Armenia2018$urban<-Armenia2018$size_5c

#Praying: Different variables from WVS-EVS. If variables ends with evs, it should be used for Armenia. 
table(Armenia2018$F028B_WVS7)
Armenia2018$pray<-Recode(Armenia2018$F028B_WVS7, "1=8;2=7;3=6;4=5;5=4;6=3;7=2; 8=1")
table(Armenia2018$pray)
```


# Variables:Armenia 2021
```{r}
## DV

#trust in religious organizations 
table(Armenia2021$Q64)
Armenia2021$rel_trust<-Recode(Armenia2021$Q64, "1=4; 2=3; 3=2; 4=1")
table(Armenia2021$rel_trust)

## IVs 

#Proud of national identity
is.na(Armenia2021$Q254) <- which(Armenia2021$Q254==5)
Armenia2021$proud_nation<-Recode(Armenia2021$Q254, "1=4; 2=3; 3=2; 4=1")
table(Armenia2021$proud_nation)



## CONTROLS 

#importance of religion in life 
table(Armenia2021$Q6)
Armenia2021$importance_rel<-Recode(Armenia2021$Q6, "1=4; 2=3; 3=2; 4=1")
table(Armenia2021$importance_rel)

#Interpersonal trust 
table(Armenia2021$Q57)
Armenia2021$inter_trust<-Recode(Armenia2021$Q57, "2=0")

#Membership to religious organizations 
table(Armenia2021$Q289CS9)
Armenia2021$rel_member<-Recode(Armenia2021$Q289CS9, "1e+07=0;2e+07=0;10100000=0; 3e+07=0; 30202001=1;30107000=0;5e+07=0;80213304=0;80400035=0;90600000=0;100000020=0; 9e+07=0")
table(Armenia2021$rel_member)

#Income level
table(Armenia2021$Q288)
Armenia2021$income<-Armenia2021$Q288

#education level
table(Armenia2021$Q275)
Armenia2021$educ<-Armenia2021$Q275
table(Armenia2021$educ)

#religiosity: attending religious services 
table(Armenia2021$Q171)
Armenia2021$religiosity<-Recode(Armenia2021$Q171, "7=1; 6=2; 5=3; 4=4; 3=5; 2=6; 1=7")
table(Armenia2021$religiosity)

#importance of traditions
table(Armenia2021$AM_QAM5_4)
is.na(Armenia2021$AM_QAM5_4) <- which(Armenia2021$AM_QAM5_4 ==-1)
is.na(Armenia2021$AM_QAM5_4) <- which(Armenia2021$AM_QAM5_4 ==-2)
Armenia2021$important_trad<-Armenia2021$AM_QAM5_4
table(Armenia2021$important_trad)

#trust in Police
table(Armenia2021$Q69)
Armenia2021$trust_police<-Recode(Armenia2021$Q69, "4=1; 3=2; 2=3; 1=4")
table(Armenia2021$trust_police)

#Trust in Government 
table(Armenia2021$Q71)
Armenia2021$trust_gov<-Recode(Armenia2021$Q71, "4=1; 3=2; 2=3; 1=4")
table(Armenia2021$trust_gov)

#Trust in Court
table(Armenia2021$Q70)
Armenia2021$trust_court<-Recode(Armenia2021$Q70, "4=1; 3=2; 2=3; 1=4")
table(Armenia2021$trust_court)

#Trust in Parliament
table(Armenia2021$Q73)
Armenia2021$trust_par<-Recode(Armenia2021$Q73, "4=1; 3=2; 2=3; 1=4")
table(Armenia2021$trust_par)

#Gender
table(Armenia2021$Q260)
Armenia2021$gender<-Armenia2021$Q260

#Age
table(Armenia2021$Q262)
Armenia2021$age<-Armenia2021$Q262

#Urban
table(Armenia2021$H_URBRURAL)
Armenia2021$urban<-Recode(Armenia2021$H_URBRURAL, "2=0")

#Praying
table(Armenia2021$Q172)
Armenia2021$pray<-Recode(Armenia2021$Q172, "1=8; 2=7;3=6;4=5;5=4;6=3;7=2;8=1")
```

# Descriptive Statsitics: Georgia 2014
```{r}

ggplot(Georgia2014, aes(x = rel_trust)) +
    geom_bar(fill = "steelblue", color = "black", width = 0.7) +
    theme_bw(base_size = 15) +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1, color = "black", size = 12),
        axis.text.y = element_text(color = "black", size = 12),
        axis.title.x = element_text(color = "black", size = 14, face = "bold"),
        axis.title.y = element_text(color = "black", size = 14, face = "bold"),
        plot.title = element_text(hjust = 0.5, color = "black", size = 16, face = "bold")
    ) +
    ggtitle("Trust in Religious Organizations in Georgia (WVS 2014)") +
    labs(y = "Frequency", x = "Trust in Religious Organizations")

```

# Descriptive Statsitics: Georgia 2018
```{r}
dv_geo2018<-Georgia2018
dv_geo2018$rel_trust<-as.numeric(dv_geo2018$rel_trust)
dv_geo2018$rel_trust<-dplyr::recode_factor(dv_geo2018$rel_trust, '1' = "None at all", '2'= "Not very much", '3' = "Quite a lot",'4' = "Great deal")
ggplot(dv_geo2018, aes(x = `rel_trust`)) +
        geom_bar()+
        theme(axis.text.x = element_text(angle = 45, hjust = 1)) +ggtitle("Trust in Georgian Orthodox Church, WVS/EVS Georgia 2018") +labs(y="Number of People", x = "")
```

# Descriptive Statsitics: Armenia
```{r}
dv_arm2021<-Armenia2021
dv_arm2021$rel_trust<-as.numeric(dv_arm2021$rel_trust)
dv_arm2021$rel_trust<-dplyr::recode_factor(dv_arm2021$rel_trust, '1' = "None at all", '2'= "Not very much", '3' = "Quite a lot",'4' = "Great deal")
ggplot(dv_arm2021, aes(x = `rel_trust`)) +
        geom_bar()+
        theme(axis.text.x = element_text(angle = 45, hjust = 1)) +ggtitle("Trust in Armenian Apostolic Church, WVS Armenia 2021") +labs(y="Number of People", x = "")
```

# Models: Georgia 2009, 2014,2018
```{r}
#2009
m1<-polr(as.factor(rel_trust)~proud_nation, data=Georgia2009, Hess = TRUE)
m2<-polr(as.factor(rel_trust)~part_nation, data=Georgia2009, Hess = TRUE)
m3<-polr(as.factor(rel_trust)~proud_nation+religiosity+inter_trust+trust_police+trust_gov+trust_court+income+educ+gender+age, data=Georgia2009, Hess = TRUE)
m4<-polr(as.factor(rel_trust)~part_nation+religiosity+inter_trust++trust_police+trust_gov+trust_court+income+educ+gender+age, data=Georgia2009, Hess = TRUE)


#2014
m5<-polr(as.factor(rel_trust)~proud_nation, data=Georgia2014, Hess = TRUE)
m6<-polr(as.factor(rel_trust)~part_nation, data=Georgia2014, Hess = TRUE)
m7<-polr(as.factor(rel_trust)~proud_nation+religiosity+inter_trust+trust_police+trust_gov+trust_court+income+educ+gender+age+urban, data=Georgia2014, Hess = TRUE)
m8<-polr(as.factor(rel_trust)~part_nation+religiosity+inter_trust+trust_police+trust_gov+trust_court+income+educ+gender+age+urban, data=Georgia2014, Hess = TRUE)


#2018
m9<-polr(as.factor(rel_trust)~proud_nation, data=Georgia2018, Hess = TRUE)
m10<-polr(as.factor(rel_trust)~proud_nation+religiosity+inter_trust+trust_police+trust_gov+trust_court+income+educ+gender+age+urban, data=Georgia2018, Hess = TRUE)



m1$AIC <- AIC(m1)
m2$AIC <- AIC(m2)
m3$AIC <- AIC(m3)
m4$AIC <- AIC(m4)
m5$AIC <- AIC(m5)
m6$AIC <- AIC(m6)
m7$AIC <- AIC(m7)
m8$AIC <- AIC(m8)
m9$AIC <- AIC(m9)
m10$AIC <- AIC(m10)


m1$BIC<-BIC(m1)
m2$BIC<-BIC(m2)
m3$BIC<-BIC(m3)
m4$BIC<-BIC(m4)
m5$BIC<-BIC(m5)
m6$BIC<-BIC(m6)
m7$BIC<-BIC(m7)
m8$BIC<-BIC(m8)
m9$BIC<-BIC(m9)
m10$BIC<-BIC(m10)

stargazer(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, ord.intercepts=T, dep.var.labels=c("Trust in Georgian Orthodox Church"), covariate.labels=c("Being Proud of Nationality", "Being Part of Nation", "Religiosity", "Interpersonal Trust", "Trust in Police", "Trust in Government", "Trust in Court", "Income", "Education", "Male(baseline:Female)", "Age", "Urban(baseline:Rural)"), type="text")
```

# Models: Armenia 2011, 2018, 2021
```{r}
#2011
m11<-polr(as.factor(rel_trust)~proud_nation, data=Armenia2011, Hess = TRUE)
m12<-polr(as.factor(rel_trust)~part_nation, data=Armenia2011, Hess = TRUE)
m13<-polr(as.factor(rel_trust)~proud_nation+religiosity+inter_trust+trust_police+trust_gov+trust_court+income+educ+gender+age+urban, data=Armenia2011, Hess = TRUE)
m14<-polr(as.factor(rel_trust)~part_nation+religiosity+inter_trust+trust_police+trust_gov+trust_court+income+educ+gender+age+urban, data=Armenia2011, Hess = TRUE)

#2018
m15<-polr(as.factor(rel_trust)~proud_nation, data=Armenia2018, Hess = TRUE)
m16<-polr(as.factor(rel_trust)~proud_nation+religiosity+inter_trust+trust_police+trust_gov+trust_court+income+educ+gender+age+urban, data=Armenia2018, Hess = TRUE)

#2021
m17<-polr(as.factor(rel_trust)~proud_nation, data=Armenia2021, Hess = TRUE)
m18<-polr(as.factor(rel_trust)~proud_nation+religiosity+inter_trust+trust_police+trust_gov+trust_court+income+educ+gender+age+urban, data=Armenia2021, Hess = TRUE)


m11$AIC <- AIC(m11)
m12$AIC <- AIC(m12)
m13$AIC <- AIC(m13)
m14$AIC <- AIC(m14)
m15$AIC <- AIC(m15)
m16$AIC <- AIC(m16)
m17$AIC <- AIC(m17)
m18$AIC <- AIC(m18)


m11$BIC <- BIC(m11)
m12$BIC <- BIC(m12)
m13$BIC <- BIC(m13)
m14$BIC <- BIC(m14)
m15$BIC <- BIC(m15)
m16$BIC <- BIC(m16)
m17$BIC <- BIC(m17)
m18$BIC <- BIC(m18)

stargazer(m11, m12, m13, m14, m15, m16, m17, m18, ord.intercepts=T, dep.var.labels=c("Trust in Armenian Apostolic Church"), covariate.labels=c("Being Proud of Nationality", "Being Part of Nation", "Religiosity", "Interpersonal Trust", "Trust in Police", "Trust in Government", "Trust in Court", "Income", "Education", "Male(baseline:Female)", "Age", "Urban(baseline:Rural)"), type="text")
```


# Predicted Probabilities: Georgia 2009
```{r}
table(Georgia2009$rel_trust)
table(Georgia2009$proud_nation)
table(Georgia2009$part_nation)
table(Georgia2009$religiosity)
table(Georgia2009$inter_trust)
table(Georgia2009$trust_police)
table(Georgia2009$trust_gov)
table(Georgia2009$trust_court)
table(Georgia2009$income)
table(Georgia2009$educ)
table(Georgia2009$gender)
table(Georgia2009$age)
table(Georgia2009$urban)


Geo2009<- data.frame(
  proud_nation= rep(seq(from = 1, to = 4, length.out = 100), 1),
  religiosity= rep(seq(from = 1, to = 7, length.out = 100), 1),
  inter_trust= rep(seq(from = 1, to =10, length.out = 100), 1),
  trust_police= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_gov= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_court= rep(seq(from = 1, to = 4, length.out = 100), 1),
  income= rep(seq(from = 1, to = 10, length.out = 100), 1),
  educ= rep(seq(from =1, to =8, length.out = 100), 1),
  gender= rep(1:2, each = 200),
  age= rep(seq(from = 18, to =91, length.out = 100), 1),
  urban= rep(seq(from = 1, to =8, length.out = 100), 1))

Geo2009<- cbind(Geo2009, predict(m3,  Geo2009, type = "probs"))
Geor2009<- melt(Geo2009, id.vars = c("proud_nation", "religiosity", "inter_trust", "trust_police", "trust_gov", "trust_court", "income", "educ", "gender", "age", "urban"),
  variable.name = "rel_trust", value.name="Probability")
Geor2009$rel_trust<-dplyr::recode_factor(Geor2009$rel_trust, '1' = "None at all", '2'= "Not very much", '3' = "Quite a lot",'4' = "Great deal")
Figure_Geo2009<-ggplot(Geor2009, aes(x=proud_nation, y = Probability, colour =rel_trust)) +
  geom_line()+
  labs(title="",
    caption="",
    x="Being Proud of Nationality", y="Probability of Trust in Georgian Orthodox Church", colour="Trust in Georgian Orthodox Church")
Figure_Geo2009


Geo_2009<- data.frame(
  part_nation= rep(seq(from = 1, to = 4, length.out =100), 4),
  religiosity= rep(seq(from = 1, to =7, length.out = 100), 4),
  inter_trust= rep(seq(from = 1, to =10, length.out = 100), 4),
  trust_police= rep(seq(from = 1, to = 4, length.out = 100), 4),
  trust_gov= rep(seq(from = 1, to = 4, length.out = 100), 4),
  trust_court= rep(seq(from = 1, to = 4, length.out = 100), 4),
  income= rep(seq(from = 1, to = 10, length.out = 100), 4),
  educ= rep(seq(from =1, to =8, length.out = 100), 4),
  gender= rep(1:2, each = 200),
  age= rep(seq(from = 18, to =91, length.out = 100), 4),
  urban= rep(seq(from = 1, to =8, length.out = 100), 4))

Geo_2009<- cbind(Geo_2009, predict(m4,  Geo_2009, type = "probs"))
Geor_2009<- melt(Geo_2009, id.vars = c("part_nation", "religiosity", "inter_trust", "trust_police", "trust_gov", "trust_court", "income", "educ", "gender", "age", "urban"),
  variable.name = "rel_trust", value.name="Probability")
Geor_2009$rel_trust<-dplyr::recode_factor(Geor_2009$rel_trust, '1' = "None at all", '2'= "Not very much", '3' = "Quite a lot",'4' = "Great deal")
Figure_Geo_2009<-ggplot(Geor_2009, aes(x=part_nation, y = Probability, colour =rel_trust)) +
  geom_line()+
  labs(title="",
    caption="",
    x="Being Part of Nation", y="Probability of Trust in Georgian Orthodox Church", colour="Trust in Religious Organizations")
Figure_Geo_2009
```


# Predicted Probabilities: Georgia 2014
```{r}
table(Georgia2014$rel_trust)
table(Georgia2014$proud_nation)
table(Georgia2014$part_nation)
table(Georgia2014$religiosity)
table(Georgia2014$inter_trust)
table(Georgia2014$trust_police)
table(Georgia2014$trust_gov)
table(Georgia2014$trust_court)
table(Georgia2014$income)
table(Georgia2014$educ)
table(Georgia2014$gender)
table(Georgia2014$age)
table(Georgia2014$urban)


Geo2014<- data.frame(
  proud_nation= rep(seq(from = 1, to = 4, length.out = 100), 4),
  religiosity= rep(seq(from = 1, to = 7, length.out = 100), 1),
  inter_trust= rep(seq(from = 1, to =10, length.out = 100), 1),
  trust_police= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_gov= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_court= rep(seq(from = 1, to = 4, length.out = 100), 1),
  income= rep(seq(from = 1, to = 10, length.out = 100), 1),
  educ= rep(seq(from =1, to =8, length.out = 100), 1),
  gender= rep(1:2, each = 200),
  age= rep(seq(from = 18, to =85, length.out = 100), 1),
  urban= rep(0:1, 200))

Geo2014<- cbind(Geo2014, predict(m7,  Geo2014, type = "probs"))
Geor2014<- melt(Geo2014, id.vars = c("proud_nation", "religiosity", "inter_trust", "trust_police", "trust_gov", "trust_court", "income", "educ", "gender", "age", "urban"),
  variable.name = "rel_trust", value.name="Probability")
Geor2014$rel_trust<-dplyr::recode_factor(Geor2014$rel_trust, '1' = "None at all", '2'= "Not very much", '3' = "Quite a lot",'4' = "Great deal")
Figure_Geo2014<-ggplot(Geor2014, aes(x=proud_nation, y = Probability, colour =rel_trust)) +
  geom_line()+
  labs(title="",
    caption="",
    x="Being Proud of Nationality", y="Probability of Trust in Georgian Orthodox Church", colour="Trust in Georgian Orthodox Church")
Figure_Geo2014


Geo_2014<- data.frame(
  part_nation= rep(seq(from = 1, to = 3, length.out = 100), 4),
  religiosity= rep(seq(from = 1, to = 7, length.out = 100), 1),
  inter_trust= rep(seq(from = 1, to =10, length.out = 100), 1),
  trust_police= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_gov= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_court= rep(seq(from = 1, to = 4, length.out = 100), 1),
  income= rep(seq(from = 1, to = 10, length.out = 100), 1),
  educ= rep(seq(from =1, to =8, length.out = 100), 1),
  gender= rep(1:2, each = 200),
  age= rep(seq(from = 18, to =85, length.out = 100), 1),
  urban= rep(0:1, 200))

Geo_2014<- cbind(Geo_2014, predict(m8,  Geo_2014, type = "probs"))
Geor_2014<- melt(Geo_2014, id.vars = c("part_nation", "religiosity", "inter_trust", "trust_police", "trust_gov", "trust_court", "income", "educ", "gender", "age", "urban"),
  variable.name = "rel_trust", value.name="Probability")
Geor_2014$rel_trust<-dplyr::recode_factor(Geor_2014$rel_trust, '1' = "None at all", '2'= "Not very much", '3' = "Quite a lot",'4' = "Great deal")
Figure_Geo_2014<-ggplot(Geor_2014, aes(x=part_nation, y = Probability, colour =rel_trust)) +
  geom_line()+
  labs(title="",
    caption="",
    x="Being Part of Nation", y="Probability of Trust in Georgian Orthodox Church", colour="Trust in Georgian Orthodox Church")
Figure_Geo_2014
```

# Predicted Probabilities: Georgia 2018
```{r}
table(Georgia2018$rel_trust)
table(Georgia2018$proud_nation)
table(Georgia2018$religiosity)
table(Georgia2018$inter_trust)
table(Georgia2018$trust_police)
table(Georgia2018$trust_gov)
table(Georgia2018$trust_court)
table(Georgia2018$income)
table(Georgia2018$educ)
table(Georgia2018$gender)
table(Georgia2018$age)
table(Georgia2018$urban)


Geo2018<- data.frame(
  proud_nation= rep(seq(from = 1, to = 4, length.out = 100), 4),
  religiosity= rep(seq(from = 1, to = 8, length.out = 100), 1),
  inter_trust= rep(0:1, each = 200),
  trust_police= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_gov= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_court= rep(seq(from = 1, to = 4, length.out = 100), 1),
  income= rep(seq(from = 1, to = 10, length.out = 100), 1),
  educ= rep(seq(from =0, to =8, length.out = 100), 1),
  gender= rep(1:2, each = 200),
  age= rep(seq(from = 18, to =82, length.out = 100), 1),
  urban= rep(seq(from = 1, to =5, length.out = 100), 1))

Geo2018<- cbind(Geo2018, predict(m10,  Geo2018, type = "probs"))
Geor2018<- melt(Geo2018, id.vars = c("proud_nation", "religiosity", "inter_trust", "trust_police", "trust_gov", "trust_court", "income", "educ", "gender", "age", "urban"),
  variable.name = "rel_trust", value.name="Probability")
Geor2018$rel_trust<-dplyr::recode_factor(Geor2018$rel_trust, '1' = "None at all", '2'= "Not very much", '3' = "Quite a lot",'4' = "Great deal")
Figure_Geo2018<-ggplot(Geor2018, aes(x=proud_nation, y = Probability, colour =rel_trust)) +
  geom_line()+
  labs(title="",
    caption="",
    x="Being Proud of Nationality", y="Probability of Trust in Georgian Orthodox Church", colour="Trust in Georgian Orthodox Church")
Figure_Geo2018
```

# Predicted Probabilities: Armenia 2011
```{r}
table(Armenia2011$rel_trust)
table(Armenia2011$proud_nation)
table(Armenia2011$part_nation)
table(Armenia2011$religiosity)
table(Armenia2011$inter_trust)
table(Armenia2011$trust_police)
table(Armenia2011$trust_gov)
table(Armenia2011$trust_court)
table(Armenia2011$income)
table(Armenia2011$educ)
table(Armenia2011$gender)
table(Armenia2011$age)
table(Armenia2011$urban)

Arm2011<- data.frame(
  proud_nation= rep(seq(from = 1, to = 4, length.out = 50), 4),
  religiosity= rep(seq(from = 1, to = 7, length.out = 100), 1),
  inter_trust= rep(0:1, each = 200),
  trust_police= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_gov= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_court= rep(seq(from = 1, to = 4, length.out = 100), 1),
  income= rep(seq(from = 1, to = 10, length.out = 100), 1),
  educ= rep(seq(from =0, to =8, length.out = 100), 1),
  gender= rep(1:2, each = 200),
  age= rep(seq(from = 18, to =85, length.out = 100), 1),
  urban= rep(seq(from = 1, to =8, length.out = 100), 1))

Arm2011<- cbind(Arm2011, predict(m13,  Arm2011, type = "probs"))
Armen2011<- melt(Arm2011, id.vars = c("proud_nation", "religiosity", "inter_trust", "trust_police", "trust_gov", "trust_court", "income", "educ", "gender", "age", "urban"),
  variable.name = "rel_trust", value.name="Probability")
Armen2011$rel_trust<-dplyr::recode_factor(Armen2011$rel_trust, '1' = "None at all", '2'= "Not very much", '3' = "Quite a lot",'4' = "Great deal")
Figure_arm2011<-ggplot(Armen2011, aes(x=proud_nation, y = Probability, colour =rel_trust)) +
  geom_line()+
  labs(title="",
    caption="",
    x="Being Proud of Nationality", y="Probability of Trust in Armenian Apostolic Church", colour="Trust in Armenian Apostolic Church")
Figure_arm2011

Arm_2011<- data.frame(
  part_nation= rep(seq(from = 1, to = 4, length.out = 50), 4),
  religiosity= rep(seq(from = 1, to = 7, length.out = 100), 1),
  inter_trust= rep(0:1, each = 200),
  trust_police= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_gov= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_court= rep(seq(from = 1, to = 4, length.out = 100), 1),
  income= rep(seq(from = 1, to = 10, length.out = 100), 1),
  educ= rep(seq(from =1, to =9, length.out = 100), 1),
  gender= rep(1:2, each = 200),
  age= rep(seq(from = 18, to =85, length.out = 100), 1),
  urban= rep(seq(from = 1, to =8, length.out = 100), 1))

Arm_2011<- cbind(Arm_2011, predict(m14,  Arm_2011, type = "probs"))
Armen_2011<- melt(Arm_2011, id.vars = c("part_nation", "religiosity", "inter_trust", "trust_police", "trust_gov", "trust_court", "income", "educ", "gender", "age", "urban"),
  variable.name = "rel_trust", value.name="Probability")
Armen_2011$rel_trust<-dplyr::recode_factor(Armen_2011$rel_trust, '1' = "None at all", '2'= "Not very much", '3' = "Quite a lot",'4' = "Great deal")
Figure_arm_2011<-ggplot(Armen_2011, aes(x=part_nation, y = Probability, colour =rel_trust)) +
  geom_line()+
  labs(title="",
    caption="",
    x="Being Part of Nation", y="Probability of Trust in Armenian Apostolic Church", colour="Armenian Apostolic Church")
Figure_arm_2011
```


# Predicted Probabilities: Armenia 2018
```{r}
table(Armenia2018$rel_trust)
table(Armenia2018$proud_nation)
table(Armenia2018$religiosity)
table(Armenia2018$inter_trust)
table(Armenia2018$trust_police)
table(Armenia2018$trust_gov)
table(Armenia2018$trust_court)
table(Armenia2018$income)
table(Armenia2018$educ)
table(Armenia2018$gender)
table(Armenia2018$age)
table(Armenia2018$urban)

Arm2018<- data.frame(
  proud_nation= rep(seq(from = 1, to = 4, length.out = 50), 1),
  religiosity= rep(seq(from = 1, to = 8, length.out = 100), 1),
  inter_trust= rep(0:1, each = 200),
  trust_police= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_gov= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_court= rep(seq(from = 1, to = 4, length.out = 100), 1),
  income= rep(seq(from = 1, to = 10, length.out = 100), 1),
  educ= rep(seq(from =0, to =8, length.out = 100), 1),
  gender= rep(1:2, each = 200),
  age= rep(seq(from = 18, to =82, length.out = 100), 1),
  urban= rep(seq(from = 1, to =5, length.out = 100), 1))

Arm2018<- cbind(Arm2018, predict(m16,  Arm2018, type = "probs"))
Armen2018<- melt(Arm2018, id.vars = c("proud_nation", "religiosity", "inter_trust", "trust_police", "trust_gov", "trust_court", "income", "educ", "gender", "age", "urban"),
  variable.name = "rel_trust", value.name="Probability")
Armen2018$rel_trust<-dplyr::recode_factor(Armen2018$rel_trust, '1' = "None at all", '2'= "Not very much", '3' = "Quite a lot",'4' = "Great deal")
Figure_arm2018<-ggplot(Armen2018, aes(x=proud_nation, y = Probability, colour =rel_trust)) +
  geom_line()+
  labs(title="",
    caption="",
    x="Being Proud of Nationality", y="Probability of Trust in Armenian Apostolic Church", colour="Trust in Armenian Apostolic Church")
Figure_arm2018
```



# Predicted Probabilities: Armenia 2021
```{r}
table(Armenia2021$rel_trust)
table(Armenia2021$proud_nation)
table(Armenia2021$religiosity)
table(Armenia2021$inter_trust)
table(Armenia2021$trust_police)
table(Armenia2021$trust_gov)
table(Armenia2021$trust_court)
table(Armenia2021$income)
table(Armenia2021$educ)
table(Armenia2021$gender)
table(Armenia2021$age)
table(Armenia2021$urban)

Arm2021<- data.frame(
  proud_nation= rep(seq(from = 1, to = 4, length.out = 100), 1),
  religiosity= rep(seq(from = 1, to = 7, length.out = 100), 1),
  inter_trust= rep(0:1, each = 200),
  trust_police= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_gov= rep(seq(from = 1, to = 4, length.out = 100), 1),
  trust_court= rep(seq(from = 1, to = 4, length.out = 100), 1),
  income= rep(seq(from = 1, to = 10, length.out = 100), 1),
  educ= rep(seq(from =0, to =8, length.out = 100), 1),
  gender= rep(1:2, each = 200),
  age= rep(seq(from = 18, to =91, length.out = 100), 1),
  urban= rep(0:1, 200))

Arm2021<- cbind(Arm2021, predict(m18,  Arm2021, type = "probs"))
Armen2021<- melt(Arm2021, id.vars = c("proud_nation", "religiosity", "inter_trust", "trust_police", "trust_gov", "trust_court", "income", "educ", "gender", "age", "urban"),
  variable.name = "rel_trust", value.name="Probability")
Armen2021$rel_trust<-dplyr::recode_factor(Armen2021$rel_trust, '1' = "None at all", '2'= "Not very much", '3' = "Quite a lot",'4' = "Great deal")
Figure_arm2021<-ggplot(Armen2021, aes(x=proud_nation, y = Probability, colour =rel_trust)) +
  geom_line()+
  labs(title="",
    caption="",
    x="Being Proud of Nationality", y="Probability of Trust in Armenian Apostolic Church", colour="Trust in Armenian Apostolic Church")
Figure_arm2021
```




# Coefficent Plots-Georgia
```{r}
mod1<-polr(as.factor(rel_trust)~proud_nation+part_nation+importance_rel+inter_trust+trust_police+trust_gov+trust_court+income+educ+gender+age+urban, data=Georgia2014, Hess = TRUE)


coef1 <- summary(mod1)$coef[1:12,1]
ses1 <- summary(mod1)$coef[1:12,2]


ylo1 <- coef1 - 1.96*ses1
yhi1 <- coef1 + 1.96*ses1
names1 <- c( "Being Proud of Nation", "Being Part of Nation", "Religiosity: Importance of Religion", "Interpersonal Trust", "Trust in Police", "Trust in Government", "Trust in Court", "Income", "Education", "Gender", "Age", "Urban")

names1 <- factor(names1, levels = rev(c("Being Proud of Nation", "Being Part of Nation", "Religiosity: Importance of Religion", "Interpersonal Trust", "Trust in Police", "Trust in Government", "Trust in Court", "Income", "Education", "Gender", "Age", "Urban")))

dfplot1 <- data.frame(names1, coef1, ylo1, yhi1)
library(ggplot2)
p1 <- ggplot(dfplot1, aes(x=names1, y=coef1, ymin=ylo1, ymax=yhi1)) + 
  geom_pointrange(colour=ifelse(ylo1 < 0 & yhi1 > 0, "grey", "black")) + 
  theme_bw() + 
  geom_hline(yintercept = 0, lty=2) +coord_flip() + xlab('') + ylab('')  +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=15,face="bold"))
p1 
```

# Coefficent Plots-Georgia 
```{r}
mod2<-polr(as.factor(rel_trust)~proud_nation+importance_rel+inter_trust+trust_police+trust_gov+trust_court+income+educ+gender+age+urban, data=Armenia2021, Hess = TRUE)

coef2 <- summary(mod2)$coef[1:11,1]
ses2 <- summary(mod2)$coef[1:11,2]


ylo2 <- coef2 - 1.96*ses2
yhi2 <- coef2 + 1.96*ses2

names2 <- c(  "Being Proud of Nation", "Religiosity: Importance of Religion" , "Interpersonal Trust", "Trust in Police", "Trust in Government", "Trust in Court", "Income", "Education", "Gender", "Age", "Urban")

names2 <- factor(names2, levels = rev(c( "Being Proud of Nation", "Religiosity: Importance of Religion", "Interpersonal Trust", "Trust in Police", "Trust in Government", "Trust in Court", "Income", "Education", "Gender", "Age", "Urban")))

dfplot2 <- data.frame(names2, coef2, ylo2, yhi2)
library(ggplot2)
p2 <- ggplot(dfplot2, aes(x=names2, y=coef2, ymin=ylo2, ymax=yhi2)) + 
  geom_pointrange(colour=ifelse(ylo2 < 0 & yhi2 > 0, "grey", "black")) + 
  theme_bw() + 
  geom_hline(yintercept = 0, lty=2) +coord_flip() + xlab('') + ylab('')  +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=15,face="bold"))
p2 
```

# Exporting data
```{r}

## you can use this code to export data in excel format to analyse in different software. 
library(writexl)
write_xlsx(x=Georgia2018, path="Georgia2018.xlsx", col_names=TRUE)
write_xlsx(x=Armenia2021, path="Armenia2021.xlsx", col_names=TRUE)
```

